Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-17 parts/example.tex
fixes & typos

We give in this section a detailed example of the use of classes of priorities
in order to model a system with temporal constraints.
This model also allows us to give a detailed example of the application of the sequential
under-approximation proposed in \pref{ssec:ordered-ua},
which consists of several applications of the methods developed in
\pref{ssec:ua}.
For this, we first have to use the flattening method presented in \pref{sec:flattening}
because the considered model contains 2 classes of priorities.

We consider in the following a model of metazoan segmentation
inspired from a first translation to Process Hitting given in~\cite{PMR10-TCSB}.
This model was originally established in silico in~\cite{MSB:MSB4100192}
in a differential equations framework.
It is composed of a wavefront gene $f$ that activates the gap-gene $a$ whose products are responsible for stripes formation.
Gene $f$ also activates a gene $c$ whose products represses the gene $a$.
The auto-inhibition of $c$ generalises a chain of repressors on $a$.
The auto-inhibition of $f$, which normally terminates
the stripes formation in the original model,
has been removed in order to focus on the stationary dynamics of the model.

The actions of the original model make $2$ classes of priorities, as represented in \pref{fig:metazoan-php}:
\begin{align*}
  \ov{\PHh}^{(1)} = \{ \quad
    & \PHfrappes{c_1}{a_1}{a_0} \quad , \quad
    \PHfrappes{f_1, c_0}{a_0}{a_1}
  \quad \} \\
  \ov{\PHh}^{(2)} = \{ \quad
    & \PHfrappem{c_1}{c_0} \quad , \quad
    \PHfrappes{f_1}{c_0}{c_1}
  \quad \} \\
\end{align*}
Indeed, without this use of priorities,
some unwanted behaviours emerge, allowing the formation of irregular stripes.
In order to fix this, a high priority is affected to the actions hitting $a$,
a low priority to the actions hitting $c$,
in order to model the fact that the switching of $c$ has to be immediately followed by
a switching of $a$.
This forces the the switches of genes $a$ and $c$
to alternate in order not to miss a stripe;
$a$ and $c$ thus have intertwined oscillations.
We can thus consider that these two classes of priorities
are derived from known reaction relative rates,
the evolution of the clock $c$ being slower and regular,
while the evolution of $a$ has to follow the changes of $c$.

@@

At this point, the static analysis results presented in
\pref{ssec:ua} can be used to check if the model is functional,
\ie if gene $a$ can oscillate, thus leading to the formation of stripes.
Starting from context $\ctx^1 = \PHstate{f_1, a_0, c_0}$,
we thus want to check the reachability of $\myp^1 = a_1$;
then, starting from any new state obtained,
we want to check the reachability of $\myp^2 = a_0$,
and finally $\myp^3 = a_1$ once again to ensure that we entered a cycle.
This consists in using \pref{th:approxinf} several times
to check these reachabilities successively,
by splitting it following \pref{ssec:ordered-ua}.

We first build the local causality graph $\thisB{\myp^1}{\ctx^1}$
related to the reachability of $\myp^1 = a_1$ from the initial state $\ctx^1$.
This graph is depicted in \pref{fig:metazoan-sa}(left).
\pref{th:approxinf} allows to conclude that this reachability is true.
One can thus extract a concretizing scenario from this local causality graph
with a traversal of the graph, as explained in \pref{ssec:concret}.
Such a traversal is detailed in \pref{tab:concret-metazoan};
the scenario extracted from this example is:
$\emptyseq \concat \emptyseq \concat \PHfrappes{c_0, f_1}{a_0}{a_1} =
\PHfrappes{c_0, f_1}{a_0}{a_1}$.
Another traversal would consist in visiting node $f_1$ before node $c_0$
when first descending from node $\{ c_0, f_1 \}$;
however, the same scenario would be extracted.
As there exists no other traversal, we thus have in this case:
$\Delta(\thisB{\myp^1}{\ctx^1}) = \{ \PHfrappes{c_0, f_1}{a_0}{a_1} \}$.

\begin{table}[htp]
  \centering
  \begin{tabular}{|c|c|c|l|l|l|}
    \hline
    \# & Dir. & Node & Marking & Output & State \\\hline\hline
    1  & $\searrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    2  & $\searrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    3  & $\searrow$ & $\xsol$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    4  & $\searrow$ & $\{ c_0, f_1 \}$ & $\{ c_0, f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    \phantom{*}%
    5* & $\searrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    6  & $\searrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    7  & $\searrow$ & $\xsol$ & $\emptyseq$ & $\emptyseq$ & $\PHstate{f_1, a_0, c_0}$ \\\hline
    8  & $\nearrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    9  & $\nearrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    10 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\{ f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
%    \phantom{*}%
    11 & $\searrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    12 & $\searrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    13 & $\searrow$ & $\xsol$ & $\emptyseq$ & $\emptyseq$ & $\PHstate{f_1, a_0, c_0}$ \\\hline
    14 & $\nearrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    15 & $\nearrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    16 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\emptyset$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    17 & $\nearrow$ & $\xsol$ & $\emptyseq$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ & $\PHstate{f_1, a_1, c_0}$ \\\hline
    18 & $\nearrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
    19 & $\nearrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
  \end{tabular}
  \caption{\label{tab:concret-metazoan}%
    Example of the extraction of a concretizing scenario
    from the local causality graph of \pref{fig:metazoan-sa}(left),
    by using the algorithm of \pref{ssec:concret}.
    The first column denotes the step number in the traversal,
    the second depicts the direction of traversal,
    either “$\searrow$” for descending or “$\nearrow$” for ascending,
    the third one is the name of the node,
    the fourth one gives the marking when the node is left,
    the fifth one gives the actions output by the algorithm
    and the last column gives the current state of the model when leaving each node.
    In step \#5, marked with an asterisk,
    the traversal visits node $c_0$, but this was arbitrarily chosen
    amongst the set $\{ c_0, f_1 \}$.
    Another traversal thus consists in visiting node $f_1$ first,
    although in this example it does not change the result.
  }
\end{table}

We denote in the following:
$\ctx^2 = \PHstate{f_1, c_0, a_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
\PHstate{f_1, c_0, a_1}$
the state resulting from the play of a scenario concretizing
$\myp^1$ in $\ctx^1$.
As explained in \pref{ssec:ordered-ua},
One can use this resulting state in order to carry on with another
successive reachability,
such as the reachability of $\myp^2 = a_0$ in this case.
The local causality graph used to check the reachability of $\myp^2$
from $ctx^2$ is given in \pref{fig:metazoan-sa}(middle).
The same reasoning allows to conclude that this reachability is true, and
to extract the following set of concretizing scenarios:
$\Delta(\thisB{\myp^2}{\ctx^2}) =
\{ \PHfrappem{a_1, f_1}{c_0}{c_1} \concat \PHfrappem{c_1}{a_1}{a_0} \}$.
We note that once again, two traversals are possible
(by visiting node $a_1$ before or after note $f_1$)
but both output the same scenario, and therefore end up in the same sate
$\ctx^3 = \PHstate{f_1, a_0, c_1}$.
Finally, the last local causality graph $\thisB{\myp^3}{\ctx^3}$,
depicted in \pref{fig:metazoan-sa}(right),
allows to conclude that this final reachability is true.

@@

    (tc10s) edge (tnc10s)
    (tnc10s) edge (ta0)
    (ta0) edge (ta00)
    (ta00) edge (ta00s)
    (ta00s) edge (tna00s)
    ;
  \end{tikzpicture}
  \caption{%
  \label{fig:metazoan-sa}%
    The three successive saturated graphs of local causality
    of the AAN in \pref{fig:metazoan-ph}
    for the objective sequence
    $\w = \PHobj{a_0}{a_1} \concat \PHobj{a_1}{a_0} \concat \PHobj{a_0}{a_1}$
    and the initial context
    $\ctx = \PHstate{a_0, c_0, f_1}$.
    The (left) graph allows to check objective $\PHobj{a_0}{a_1}$
    from the initial context $\ctx$.
    The (middle) graph is for the objective $\PHobj{a_1}{a_0}$
    and the context $\PHstate{a_1, c_0, f_1}$.
    The (right) graph is for the last objective, $\PHobj{a_0}{a_1}$,
    and the context $\PHstate{a_0, c_1, f_1}$.
  }
\end{figure}

@@

In order to support the scalability and applicability of our under-approximation of reachability, we
apply our new approach to the analysis of two large-scale models:
a T-cell receptor (TCR) signalling pathway~\cite{tcrsig94}
and an epidermal growth factor receptor (EGFR) signalling pathway~\cite{Samaga2009}.
These models both gather around a hundred components and are detailed below.
They are originally specified as Boolean networks,
and have been automatically encoded into
a Process Hitting model with two classes of priorities,
whose dynamics is equivalent to an AAN%
\footnote{Files are available at
\url{http://maxime.folschette.name/underapprox-aan.zip}. \todo{Mettre en ligne}}.
Boolean networks being a subclass of AANs, this translation is straightforward.
In the following, we first present the Pint implementation,
then the two models that were used for our tests,
and the finally summarise the quantitative results of these tests.

@@

The under-approximation presented in \pref{sec:sa} has been implemented
in the existing Pint software%
\footnote{Pint gathers tools related to the Process Hitting
and is freely available at \url{http://loicpauleve.name/pint}.
The release “2015-02-11” was used for these experiments.}.
It comes in two versions:
\begin{itemize}
  \item One version consists in building the local causality graph once
    and checking \pref{th:approxinf} on this graph only.
    This version is polynomial in the size of the model,
    and therefore scalable by nature by its low complexity.
    However, it may be non-conclusive due to the presence of cycles
    or dependent synchronizations that could be avoided.
  \item The other version consists in checking \pref{th:approxinf}
    on every sub-graph obtained by considering sub-sets of the nodes in $\Sol$
    of the local causality graph.
    This enumeration of “sub-solutions” may allow to find conclusive
    responses by removing cycles or unnecessary local states in the graph.
    However, due to its exhaustive nature,
    it is exponential in the number of solutions of each objective,
    and thus not as scalable.
\end{itemize}
In other words, when this implementation is unable to conclude with the
local causality graph alone, it tries to enumerate sub-solutions
in order to reach a conclusion.
Although this search is guided in order to remove in priority
the solutions that could create cycles or depended synchronizations,
in the worst case all combinations have to be checked.
Therefore, for the following tests, we capped the execution time
of each call to Pint to 3 seconds,
considering that the implementation is inconclusive above this threshold.

@@

The TCR signalling pathway consists of 94 components.
We checked the reachability for the independent activation of
4 outputs of the signalling cascade (SRE, AP1, NFkB, NFAT)
for all possible combinations of the 3 inputs (CD4, CD28, TCRlig).
All result in conclusive decisions,
and our under-approximation has been satisfied in 12 cases (over
32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
(and non-satisfiability in the other cases, using the previously existing over-approximation).

>>>>

We give in this section a detailed example of the use of classes of priorities
in order to model a system with temporal constraints.
This model also allows us to give a detailed example of the application of the sequential
under-approximation proposed in \pref{ssec:ordered-ua},
which consists of several applications of the method developed in
\pref{ssec:ua}.
For this, we first have to use the flattening method presented in \pref{sec:flattening}
because the considered model contains 2 classes of priorities.

We consider in the following a model of metazoan segmentation
inspired from a first translation to Process Hitting model given in~\cite{PMR10-TCSB}.
This model was originally established in silico in~\cite{MSB:MSB4100192}
in a differential equations framework.
It is composed of a wavefront gene $f$ that activates the gap-gene $a$ whose products are responsible for stripes formation.
Gene $f$ also activates a gene $c$ whose products represses the gene $a$.
The auto-inhibition of $c$ generalises a chain of repressors on $a$.
The auto-inhibition of $f$, which normally terminates
the stripes formation in the original model,
has been removed in order to focus on the stationary dynamics of the model.

The actions of the original model make $2$ classes of priorities, as represented in \pref{fig:metazoan-php}:
\begin{align*}
  \ov{\PHh}^{(1)} = \{ \quad
    & \PHfrappes{c_1}{a_1}{a_0} \quad , \quad
    \PHfrappes{f_1, c_0}{a_0}{a_1}
  \quad \} \\
  \ov{\PHh}^{(2)} = \{ \quad
    & \PHfrappem{c_1}{c_0} \quad , \quad
    \PHfrappes{f_1}{c_0}{c_1}
  \quad \} \\
\end{align*}
Indeed, without this use of priorities,
some unwanted behaviours emerge, allowing the formation of irregular stripes.
In order to fix this, a high priority is affected to the actions hitting $a$
and a low priority to the actions hitting $c$,
in order to model the fact that the switching of $c$ has to be immediately followed by
a switching of $a$.
This forces the the evolution of genes $a$ and $c$
to alternate in order not to miss a stripe;
$a$ and $c$ thus have intertwined oscillations.
We can thus consider that these two classes of priorities
are derived from known relative reaction rates,
the evolution of the clock $c$ being slower and regular,
while the evolution of $a$ has to follow the changes of $c$.

@@

At this point, the static analysis results presented in
\pref{ssec:ua} can be used to check if the model is functional,
\ie if gene $a$ can oscillate, thus leading to the formation of stripes.
Starting from context $\ctx^1 = \PHstate{f_1, a_0, c_0}$,
we thus want to check the reachability of $\myp^1 = a_1$;
then, starting from any new state obtained,
we want to check the reachability of $\myp^2 = a_0$,
and finally $\myp^3 = a_1$ once again to ensure that we entered a cycle.
This consists in using \pref{th:approxinf} several times
to check these reachabilities successively,
by splitting it following the method given in \pref{ssec:ordered-ua}.

We first build the local causality graph $\thisB{\myp^1}{\ctx^1}$
related to the reachability of $\myp^1 = a_1$ from the initial state $\ctx^1$.
This graph is depicted in \pref{fig:metazoan-sa}(left).
\pref{th:approxinf} allows to conclude that this reachability is true.
One can thus extract a concretizing scenario from this local causality graph
with a traversal of the graph, as explained in \pref{ssec:concret}.
Such a traversal is detailed in \pref{tab:concret-metazoan};
the scenario extracted from this example consists of only one action:
$\PHfrappes{c_0, f_1}{a_0}{a_1}$.
Another traversal of the same graph
would consist in visiting node $f_1$ before node $c_0$
when first descending from node $\{ c_0, f_1 \}$;
however, the same scenario would be extracted.
As there exists no other traversal, we thus have in this case:
$\Delta(\thisB{\myp^1}{\ctx^1}) = \{ \PHfrappes{c_0, f_1}{a_0}{a_1} \}$.

We denote in the following:
$\ctx^2 = \PHstate{f_1, a_0, c_0} \play \PHfrappes{c_0, f_1}{a_0}{a_1} =
\PHstate{f_1, a_1, c_0}$
the state resulting from the play of the scenario concretizing
$\myp^1$ in $\ctx^1$.
As explained in \pref{ssec:ordered-ua},
one can use this resulting state in order to carry on with another
successive reachability,
such as the reachability of $\myp^2 = a_0$ in our case.
The local causality graph used to check the reachability of $\myp^2$
from $\ctx^2$ is given in \pref{fig:metazoan-sa}(middle).
The same reasoning allows to conclude that this reachability is true, and
to extract the following set containing only one concretizing scenario:
$\Delta(\thisB{\myp^2}{\ctx^2}) =
\{ \PHfrappes{a_1, f_1}{c_0}{c_1} \concat \PHfrappes{c_1}{a_1}{a_0} \}$.
We note that once again, two traversals are possible
(by visiting node $a_1$ before or after note $f_1$)
but both output the same scenario, and therefore end up in the same sate
$\ctx^3 = \PHstate{f_1, a_0, c_1}$.
Finally, the last local causality graph $\thisB{\myp^3}{\ctx^3}$,
depicted in \pref{fig:metazoan-sa}(right),
allows to conclude that this final reachability is true.

@@

    (tc10s) edge (tnc10s)
    (tnc10s) edge (ta0)
    (ta0) edge (ta00)
    (ta00) edge (ta00s)
    (ta00s) edge (tna00s)
    ;
  \end{tikzpicture}
  \caption{%
  \label{fig:metazoan-sa}%
    The three successive saturated graphs of local causality
    of the AAN in \pref{fig:metazoan-ph}
    for the successive reachability of $a_0$, $a_1$ and $a_0$
    from the initial context
    $\ctx = \PHstate{f_1, a_0, c_0}$.
    The (left) graph allows to check the reachability of $a_1$
    from the initial context $\ctx$.
    The (middle) graph is for the reachability of $a_0$
    and the context $\PHstate{f_1, a_1, c_0}$.
    The (right) graph is for the last reachability, $a_1$,
    and the context $\PHstate{f_1, a_0, c_1}$.
  }
\end{figure}

\begin{table}[p]
  \centering
  \begin{tabular}{|c|c|c|l|l|l|}
    \hline
    \# & Dir. & Node & Marking & Output & State \\\hline\hline
    1  & $\searrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    2  & $\searrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    3  & $\searrow$ & $\xsol$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    4  & $\searrow$ & $\{ c_0, f_1 \}$ & $\{ c_0, f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    \phantom{*}%
    5* & $\searrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    6  & $\searrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    7  & $\searrow$ & $\xsol$ & $\emptyseq$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    8  & $\nearrow$ & $\PHobj{c_0}{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    9  & $\nearrow$ & $\xproc{c_0}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    10 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\{ f_1 \}$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
%    \phantom{*}%
    11 & $\searrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    12 & $\searrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    13 & $\searrow$ & $\xsol$ & $\emptyseq$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    14 & $\nearrow$ & $\PHobj{f_1}{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    15 & $\nearrow$ & $\xproc{f_1}$ &  &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    16 & $\nearrow$ & $\{ c_0, f_1 \}$ & $\emptyset$ &  & $\PHstate{f_1, a_0, c_0}$ \\\hline
    17 & $\nearrow$ & $\xsol$ & $\emptyseq$ & $\PHfrappes{c_0, f_1}{a_0}{a_1}$ & $\PHstate{f_1, a_1, c_0}$ \\\hline
    18 & $\nearrow$ & $\PHobj{a_0}{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
    19 & $\nearrow$ & $\xproc{a_1}$ &  &  & $\PHstate{f_1, a_1, c_0}$ \\\hline
  \end{tabular}
  \caption{\label{tab:concret-metazoan}%
    Example of the extraction of a concretizing scenario
    from the local causality graph of \pref{fig:metazoan-sa}(left),
    by using the algorithm of \pref{ssec:concret}.
    The first column denotes the step number in the traversal,
    the second depicts the direction of traversal,
    either “$\searrow$” for descending or “$\nearrow$” for ascending,
    the third one is the name of the current node,
    the fourth one gives the marking of this node when it is left,
    the fifth one gives the actions output by the algorithm
    and the last column gives the current state of the model when leaving each node.
    In step \#5, marked with an asterisk,
    the traversal visits node $c_0$, but this was arbitrarily chosen
    amongst the set $\{ c_0, f_1 \}$.
    Another traversal thus consists in visiting node $f_1$ first,
    although in this example it does not change the result.
  }
\end{table}

@@

In order to support the scalability and applicability of our under-approximation of reachability, we
apply our new approach to the analysis of two large-scale models:
a T-cell receptor (TCR) signalling pathway~\cite{tcrsig94}
and an epidermal growth factor receptor (EGFR) signalling pathway~\cite{Samaga2009}.
These models both gather about a hundred components and are detailed below.
They are originally specified as Boolean networks,
and have been automatically encoded into
a Process Hitting model with two classes of priorities,
whose dynamics is equivalent to an AAN%
\footnote{Files are available at
\url{http://maxime.folschette.name/underapprox-aan.zip}. \todo{Mettre en ligne}}.
Boolean networks being a subclass of AANs, this translation is straightforward.
In the following, we first present the Pint implementation,
then the two models that were used for our tests,
and the finally summarise the quantitative results of these tests.

@@

The under-approximation presented in \pref{sec:sa} has been implemented
in the existing Pint software%
\footnote{Pint gathers tools related to the Process Hitting
and is freely available at \url{http://loicpauleve.name/pint}.
The release “2015-02-11” was used for these experiments.}.
It comes in two versions:
\begin{itemize}
  \item One version consists in building the local causality graph once
    and checking \pref{th:approxinf} on this graph only.
    This version is polynomial in the size of the model,
    and therefore scalable by nature by its low complexity.
    However, it may be non-conclusive due to the presence of cycles
    or non-independent synchronizations that could be avoided.
  \item The other version consists in checking \pref{th:approxinf}
    on every sub-graph obtained by considering sub-sets of the nodes in $\Sol$
    of the local causality graph.
    This enumeration of “sub-solutions” may allow to find conclusive
    responses by removing cycles or unnecessary local states in the graph.
    However, due to its exhaustive nature,
    it is exponential in the number of solutions of each objective,
    and thus not as scalable.
\end{itemize}
In other words, when this implementation is unable to conclude with the
local causality graph alone, it tries to enumerate sub-solutions
in order to reach a conclusion.
Although this search is guided in order to remove in priority
the solutions that could create cycles or depended synchronizations,
in the worst case all combinations have to be checked.
Therefore, for the following tests, we capped the execution time
of each call to Pint to 3 seconds,
considering that the implementation is inconclusive above this threshold.

@@

The TCR signalling pathway consists of 94 components.
We checked the reachability for the independent activation of
the 4 outputs of the signalling cascade (SRE, AP1, NFkB, NFAT)
for all possible combinations of the 3 inputs (CD4, CD28, TCRlig).
All result in conclusive decisions,
and our under-approximation has been satisfied in 12 cases (over
32) proving the satisfiability of the concerned reachability property in the encoded Boolean network
(and non-satisfiability in the other cases, using the previously existing over-approximation).
